\section{Lessons and Skills Gained} 
After spending three months with Grit Systems Engineering, \cite{eagle} Lagos, and another three months with the Microelectronics research group, saying I gained a lot of experience is an understatement. Some of the skills that were acquired are discussed below.
\begin{enumerate}
\item \textbf{Linking of school work and Industrial work}: This was a very prominent and important lesson learnt during the course of this program. Having spent four years in school studying different part of electronics, SIWES gave me the opportunity to participate actively in device design and production. All concepts ranging from communication, Digital systems, Computational and system architecture that we have been taught in school played a very important role in making designing systems and products based on these concepts easy. This has made of me, a better engineer and a increasingly curious student.
\item \textbf{Application of safe working practices}: Throughout the period of attachment, I was able apply the safe working practices I
learnt during the whole training period. I was able apply the Electrostatic discharge guidelines which gave more protection from damages to circuit boards. Also, I learnt to use gas masks, fume extractors and protective goggles when soldering and drilling in the workshop.

\item \textbf{Teamwork}: Grit Systems is made up of two teams: hardware and software. I was in the hardware team throughout my stay in the company. In the company, all teams made use of trello which aided communication and tracking of activities. I was able to improve my
communication skills and ability to relate with people. I developed the ability to design systems with great modularity and ease of use for the non-hardware part of the team. 

\item \textbf{Understanding of the principles of operation of the tools used by the company}: By the end of the attachment, I was able to gain a sound understanding of the principles behind the operations of most of the tools used by the company such as drilling machines, soldering station, oscilloscopes and clamp multimeters. Also, I got familiarized with current transformers and their calibration.

\end{enumerate}